Yeast Deamination Sequence and Position Figure Generation

### 2022-06-15 R/ArabidopsisDeaminationAnchoredExcisionSiteFigureGeneration.rmd
Added various filtered plots

>>>>

```{r CPD_sequence_frequencies_filtered, fig.width = 5, fig.height = 8}
min5PrimeCutSiteDistance = 15
max5PrimeCutSiteDistance = 25
for (i in seq_along(threePrimeMMAnchoredSixFourSeqFreq)) {
  plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq[[i]]$ZT2,
                          title = paste(c("CPD", titleCaseFiltering,
                                          "3' Anchored YR Freq", repNames[i]), collapse = ' '),
                          secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                          expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"),
                          minReadLength = min5PrimeCutSiteDistance,
                          max5PrimeCutSiteDistance = max5PrimeCutSiteDistance)
}
```

### 2022-06-15 R/ArabidopsisDeaminationSequenceAndPositionFigureGeneration.rmd
Added various filtered plots

@@

>>>>

```{r CPD_mismatch_position_frequencies_by_read_length_filtered, fig.width = 5, fig.height = 5}
for (i in seq_along(CPDMismatchData)) {
  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]$`ZT2`, includedTypes = c("C>T"),
                                           title = paste(c("CPD", titleCaseFiltering,
                                                           "C>T Mismatch Pos Freq", repNames[i]), collapse = ' '),
                                           zScoreTables = CPDMMFreqZScores[[i]])
  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]$`ZT2`, includedTypes = c("C>T"),
                                           title = paste(c("CPD", titleCaseFiltering,
                                                           "C>T Mismatch Pos Freq", repNames[i]), collapse = ' '),
                                           zScoreTables = CPDMMFreqZScores[[i]], posType = FIVE_PRIME)
}
```

@@

```{r CPD_position_differences_across_read_lengths_filtered, fig.width = 9, fig.height = 5}
for (i in seq_along(CPDGroupedStats)) {
  plotGroupedPositionStats(CPDGroupedStats[[i]]$three_prime[Timepoint == "ZT2"],
                           CPDGroupedStats[[i]]$five_prime[Timepoint == "ZT2"],
                           POS_DIFF, title = paste(c("CPD", titleCaseFiltering,
                                                     "C>T Mismatch Pos Diff", repNames[i]), collapse = ' '),
                           xAxisBreaks = c(minReadLength:maxReadLength))
}
```

### 2022-06-15 R/NHF1DeaminationAnchoredExcisionSiteFigureGeneration.rmd
Added various filtered plots

@@

@@

>>>>

```{r CPD_mismatch_anchored_nucleotide_frequencies_filtered_x2, fig.width = 5, fig.height = 8}
min3PrimeCutSiteDistance = 1
max3PrimeCutSiteDistance = 12

for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq[[i]][Timepoint == "1h"], 
                                 title = paste(c("CPD", titleCaseFiltering,
                                                 "5' Anchored Nuc Freq", repNames[i]), collapse = ' '),
                                 yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                                 posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
                                 expansionOffset = expansionOffset,
                                 minReadLength = min3PrimeCutSiteDistance, maxReadLength = max3PrimeCutSiteDistance)
}
```

@@

```{r CPD_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 9}
min5PrimeCutSiteDistance = 13
max5PrimeCutSiteDistance = 25

for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq[[i]], 
                                 title = paste(c("CPD", titleCaseFiltering,
                                                 "5' Anchored Purine Freq", repNames[i]), collapse = ' '),
                                 yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                                 combineNucleotides = c("AG"), combinedNames = c("Purine"),
                                 posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
                                 expansionOffset = expansionOffset,
                                 minReadLength = min5PrimeCutSiteDistance, maxReadLength = max5PrimeCutSiteDistance)
}
```

```{r CPD_mismatch_anchored_purine_frequencies_x2, fig.width = 5, fig.height = 9}
min5PrimeCutSiteDistance = 13
max5PrimeCutSiteDistance = 25

for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq[[i]][Timepoint == "1h"], 
                                 title = paste(c("CPD", titleCaseFiltering,
                                                 "5' Anchored Purine Freq", repNames[i]), collapse = ' '),
                                 yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                                 combineNucleotides = c("AG"), combinedNames = c("Purine"),
                                 posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
                                 expansionOffset = expansionOffset,
                                 minReadLength = min5PrimeCutSiteDistance, maxReadLength = max5PrimeCutSiteDistance)
}
```

@@

```{r CPD_sequence_frequencies_filtered, fig.width = 11, fig.height = 8}
min5PrimeCutSiteDistance = 13
max5PrimeCutSiteDistance = 25
for (i in seq_along(threePrimeMMAnchoredSixFourSeqFreq)) {
  plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq[[i]],
                          title = paste(c("CPD", titleCaseFiltering,
                                          "3' Anchored YR Freq", repNames[i]), collapse = ' '),
                          secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                          expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"),
                          minReadLength = min5PrimeCutSiteDistance,
                          max5PrimeCutSiteDistance = max5PrimeCutSiteDistance)
}
```

```{r CPD_sequence_frequencies_filtered_x2, fig.width = 5, fig.height = 8}
min5PrimeCutSiteDistance = 13
max5PrimeCutSiteDistance = 25
for (i in seq_along(threePrimeMMAnchoredSixFourSeqFreq)) {
  plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq[[i]]$`1h`,
                          title = paste(c("CPD", titleCaseFiltering,
                                          "3' Anchored YR Freq", repNames[i]), collapse = ' '),
                          secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                          expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"),
                          minReadLength = min5PrimeCutSiteDistance,
                          max5PrimeCutSiteDistance = max5PrimeCutSiteDistance)
}
```

### 2022-06-15 R/NHF1DeaminationSequenceAndPositionFigureGeneration.rmd
Added various filtered plots

@@

>>>>

```{r CPD_mismatch_position_frequencies_by_read_length_filtered, fig.width = 5, fig.height = 5}
for (i in seq_along(CPDMismatchData)) {
  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]$`1h`, includedTypes = c("C>T"),
                                           title = paste(c("CPD", titleCaseFiltering,
                                                           "C>T Mismatch Pos Freq", repNames[i]), collapse = ' '),
                                           zScoreTables = CPDMMFreqZScores[[i]])
  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]$`1h`, includedTypes = c("C>T"), posType = FIVE_PRIME,
                                           title = paste(c("CPD", titleCaseFiltering,
                                                           "C>T Mismatch Pos Freq", repNames[i]), collapse = ' '),
                                           zScoreTables = CPDMMFreqZScores[[i]])
}
```

@@

```{r CPD_position_differences_across_read_lengths_filtered, fig.width = 9, fig.height = 5}
for (i in seq_along(CPDGroupedStats)) {
  plotGroupedPositionStats(CPDGroupedStats[[i]]$three_prime[Timepoint == "1h"],
                           CPDGroupedStats[[i]]$five_prime[Timepoint == "1h"],
                           POS_DIFF, title = paste(c("CPD", titleCaseFiltering,
                                                     "C>T Mismatch Pos Diff", repNames[i]), collapse = ' '),
                           xAxisBreaks = c(minReadLength:maxReadLength))
}
```

### 2022-06-15 R/NHF1GeneralReadSequenceFigureGeneration.rmd
Added various filtered plots

>>>>

```{r CPD_sequence_frequencies_filtered_x2, fig.width = 5, fig.height = 9}
minReadLength = 18
for (i in seq_along(CPDTGGSeqFreq)) {
  plotSequenceFrequencies(CPDTGGSeqFreq[[i]]$`1h`, title = paste("CPD TGG Frequencies", repNames[i]),
                          expansionOffset = expansionOffset, showThreePrimeCutSite = TRUE,
                          showFivePrimeCutSite = TRUE, querySequences = c("TGG"), minReadLength = minReadLength)
}

for (i in seq_along(CPDCGASeqFreq)) {
  plotSequenceFrequencies(CPDCGASeqFreq[[i]]$`1h`, title = paste("CPD CGA Frequencies", repNames[i]),
                          expansionOffset = expansionOffset, showThreePrimeCutSite = TRUE,
                          showFivePrimeCutSite = TRUE, querySequences = c("CGA"), minReadLength = minReadLength)
}
```

### 2022-06-15 R/YeastDeaminationAnchoredExcisionSiteFigureGeneration.rmd
Added various filtered plots

>>>>

```{r CPD_sequence_frequencies_filtered, fig.width = 11, fig.height = 8}
min5PrimeCutSiteDistance = 11
max5PrimeCutSiteDistance = 19
for (i in seq_along(threePrimeMMAnchoredSixFourSeqFreq)) {
  plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq[[i]],
                          title = paste(c("CPD", titleCaseFiltering,
                                          "3' Anchored YR Freq", repNames[i]), collapse = ' '),
                          secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                          expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"),
                          minReadLength = min5PrimeCutSiteDistance,
                          max5PrimeCutSiteDistance = max5PrimeCutSiteDistance)
}
```

```{r CPD_sequence_frequencies_filtered_x2, fig.width = 5, fig.height = 8}
min5PrimeCutSiteDistance = 11
max5PrimeCutSiteDistance = 19
for (i in seq_along(threePrimeMMAnchoredSixFourSeqFreq)) {
  plotSequenceFrequencies(threePrimeMMAnchoredCPDSeqFreq[[i]]$`20min`,
                          title = paste(c("CPD", titleCaseFiltering,
                                          "3' Anchored YR Freq", repNames[i]), collapse = ' '),
                          secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                          expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"),
                          minReadLength = min5PrimeCutSiteDistance,
                          max5PrimeCutSiteDistance = max5PrimeCutSiteDistance)
}
```

### 2022-06-15 R/YeastDeaminationSequenceAndPositionFigureGeneration.rmd
Added various filtered plots

@@

>>>>

```{r CPD_mismatch_position_frequencies_by_read_length_filtered, fig.width = 5, fig.height = 5}
for (i in seq_along(CPDMismatchData)) {
  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]$`20min`, includedTypes = c("C>T"),
                                           title = paste(c("CPD", titleCaseFiltering,
                                                           "C>T Mismatch Pos Freq", repNames[i]), collapse = ' '),
                                           zScoreTables = CPDMMFreqZScores[[i]])
  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]$`20min`, includedTypes = c("C>T"),
                                           title = paste(c("CPD", titleCaseFiltering,
                                                           "C>T Mismatch Pos Freq", repNames[i]), collapse = ' '),
                                           zScoreTables = CPDMMFreqZScores[[i]], posType = FIVE_PRIME)
}
```

@@

```{r CPD_position_differences_across_read_lengths_filtered, fig.width = 9, fig.height = 5}
for (i in seq_along(CPDGroupedStats)) {
  plotGroupedPositionStats(CPDGroupedStats[[i]]$three_prime[Timepoint == "20min"],
                           CPDGroupedStats[[i]]$five_prime[Timepoint == "20min"],
                           POS_DIFF, title = paste(c("CPD", titleCaseFiltering,
                                                     "C>T Mismatch Pos Diff", repNames[i]), collapse = ' '),
                           xAxisBreaks = c(minReadLength:maxReadLength))
}
```
